Coherent optical creation of a single molecule -- Supplemental material

### 2021-05-10 sm.tex
Update on Overleaf.

\section{Calculating Matrix Elements with Coupled Channel Ground State}
To calculate Rabi frequencies for transitions to the eight excited molecular potentials, we
obtain their wavefunctions from a single-channel calculation \cite{Fattal1996} using the potential energy curves described in section \ref{sm:excited_states}. We
then calculate overlap integrals between these functions and either the triplet ($S=1$) or singlet ($S=0$) components of the
coupled-channel wavefunctions for either the target molecular state or the confined atomic state.
These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments~\footnote{Private communication with R. Moszynski}.

@@

>>>>

\section{Calculating Matrix Elements with Coupled Channel Ground State}
To calculate Rabi frequencies for transitions to the eight excited molecular potentials, we
obtain their wavefunctions from a single-channel calculation \cite{Fattal1996} using the potential energy curves described in section \ref{sm:excited_states}. We
then calculate overlap integrals between these functions and either the triplet ($S=1$) or singlet ($S=0$) components of the
coupled-channel wavefunctions for either the target molecular state or the confined atomic state.
These calculations assume that the intermediate states have pure singlet or triplet character and neglect its
nuclear spin character, which is unknown. These calculations include theoretical electronic transition dipole moments shown in figure \ref{tdm-sm} calculated with ab initio methods~\footnote{Private communication with R. Moszynski}.

@@

\begin{figure}[ht!]
  \includegraphics[width=\textwidth]{imgs/TDM_wide.pdf}
  \caption{Electronic transition dipole moments calculated via ab initio methods between different electronic states of NaCs. These transition dipole moments are shown as a function of internuclear distance.
    \label{tdm-sm}}
\end{figure}
